% monitoring_system.tex
\textbf{\Large Actors}
\begin{itemize}
    \item \textbf{Primary Actor:} Refinery Operator
    \item \textbf{Secondary Actors:} UAV, UGV
\end{itemize}

\textbf{\Large Basic Flow}
\begin{itemize}
    \item \textbf{Operator Initiates Monitoring:}
    \begin{itemize}
        \item Operator starts the monitoring system, which triggers the UAV to begin its patrol.
    \end{itemize}
%second point
    \item \textbf{UAV Patrols Refinery:}
    \begin{itemize}
        \item UAV autonomously flies predefined routes, capturing real-time video and sensor data.
        \item UAV uses computer vision algorithms to detect anomalies, such as:
        \begin{itemize}
            \item Unusual roof movement of floating storage tanks
            \item Spills or leaks
            \item Unauthorized personnel or vehicles
        \end{itemize}
    \end{itemize}
%third point
    \item \textbf{Anomaly Detection:}
    \begin{itemize}
        \item If an anomaly is detected, the UAV alerts the operator and the UGV.
    \end{itemize}
%fourth point
    \item \textbf{Anomaly Detection:}
    \begin{itemize}
        \item UAV adjusts its flight path to focus on the anomaly area, capturing detailed images and videos.
        \item UGV is dispatched to the ground-level location indicated by the UAV, using the real-time data to navigate.
    \end{itemize}
%fifth point
    \item \textbf{Operator Assessment and Response:}
    \begin{itemize}
        \item Operator reviews the data from the UAV and UGV to assess the severity of the situation.
        \item Based on the assessment, the operator may:
        \begin{itemize}
            \item Dispatch emergency response teams
            \item Activate safety protocols
            \item Implement corrective actions
        \end{itemize}
    \end{itemize}
%sixth point
    \item \textbf{Continuous Monitoring:}
    \begin{itemize}
        \item The UAV and UGV continue to monitor the situation, providing real-time updates to the operator.
        \item The system adapts to changing conditions, adjusting flight paths and ground-level inspections as needed.
    \end{itemize}
\end{itemize}
